---
title: "Robot Gastrectomy"
author: "JCSalo"
date: "May 19, 2017"
output:
  pdf_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## R Markdown

Anesthesia: General anesthesia with single-lumen ET tube. 

Antibiotics: [Invanz 1 gram] administered IV prior to incision.

Position:  Supine with left arm abducted on arm board and right arm tucked. Reverse trendelenburg position.  Table rotated to allow for docking of robot.

Prep:  Foley catheter. Hair cleared from operative field with electric clippers.  Skin prep with [Chloroprep followed by 3 minute drying time]. Sterile drape.

Time Out: A World Health Organization Surgical Time-Out was performed in accordance with CHS guidelines.m[

Initial Endoscopy: ][  ][Injection of indocyanine green ][suspended in albumin][ was performed around the tumor.]

Place NG tube

Place Dobhoff tube

Mark proximal aspect of tumor with Resolution Clip x2.  Leave last resolution clip attached (do not eject).  Withdraw scope to esophagus.

Abdominal Access: Abdominal access with GelPort just cephelad to umbilicus (will be used for robotic camera)

Ports: 

Extended 8mm port through Gel Port

8mm port mid-LUQ

8/13mm stapler port lateral LUQ

8mm port mid-RUQ

12mm assisting port R mid-quadrant medial to 8mm mid-RUQ robotic port

5mm port lateral RUQ for Nathanson liver retractor.

Suspend falciform with 0 Silk on Keith needle.

Divide gastrocolic omentum to get access to lesser sac


Fenestrate transverse mesocolon to left of MCA


Mark jejunum at 20,35,60cm with blue marker

stay sutures from 20-60cm at inferior aspect of Braun

Directional suture at 35cm (long) (?pexy suture to posterior stomach)




Robot: DaVinci [Xi] robot docked. [with Graptor in Arm 3 and fenestrated bipolar in Arm 2 and monopolar scissors in Arm 1].

Gastric Mobilization: Greater curvature mobilized with bipolar and monopolar cautery. Gastrocolic omentum incised. 

Distal Dissection:  Right gastroepiploic artery and vein dissected free and infrapyloric nodes (Station 6) taken with the specimen. [Right gastroepiploic artery and vein cliped with Weck clips]. Right gastric artery nodes (Station5) taken with specimen. [Right gastric artery clipped with Weck clips]

Central Node Dissection:  Left gastric artery nodes (Station 7) nodes harvested.  [Common hepatic (Station 8) nodes harvested.][ Hepatoduodenal ligament nodes along the left side (Station 12) harvested.][ Celiac trunk (Station 9) nodes harvested.] [Proximal splenic artery nodes harvested (Station 11).][ Left gastric artery divided at origin with Weck clips][ Main trunk of left gastric artery left intact after dissecting nodes.][ Left gastric artery preserved to supply a replaced left gastric artery.][Ascending branch of left gastric artery preserved.][-- Comment on clinical node involvement--]

Distal Resection: [Duodenum transected with linear stapler 3.5mm Blue load ][using robotic stapler.][using endoGIA.]

Proximal Resection: [Proximal resection ][ using robotic stapler4.8mm Green load.][ using endoGIA Medium-Thick load.] [Specimen placed in a bag and retrieved through the umbilical port.][

Specimen Retrieval: [ Robot undocked and umbilical port enlarged to extract specimen.][ Extraction site closed with interrupted 0 Vicryl suture.][

Frozen Section:] []
 
Reconstruction: [Retrocolic anastomosis with jejunum brought through fenestration in the transverse mesocolon.] [Bilroth II anastomosis constructed with a robotic 3.5mm Blue load stapler. Defect closed with a 6"6" V-Loc CV23 suture (CLOVL0804).]  [Robotic sutured anastomosis with  6" V-Loc CV23 suture (CLOVL0804) ] [Circular stapled anastomosis with 25mm OrVil and DST XL stapler introduced into the Roux-en-Y limb.  Defect closed with 3.5mm linear stapler.] [ 

Leak test with bubbling using EGD scope showed no evidence of leak.][Leak test with methylene blue showed no evidence of leak.][

Braun enteroenterostomy constructed with a 3.5mm linear stapler and the defect closed with a 6" V-Loc CV23 suture (CLOVL0804).][

Roux-en-Y enteroenterostomy constructed with a 3.5mm linear stapler and the defect closed with a 6" V-Loc CV23 suture (CLOVL0804).][

Nasogastric tube was placed [by Anesthesia.][with the assistance of and EGD scope.]

Drains: []

Closure: [12mm assisting port closed with 0 Vicryl.][ 13mm stapler port closed with 0 Vicryl.]  Abdomen desufflated and incisions closed [with 4-0 Monocryl][ with staples].

Specimens:  []

Complications: [ None ]

Contamination: [Clean-Contaminated, due to entry into the GI tract (stomach).]

Estimated Blood Loss (EBL): [|--EBL--|] [


```{r cars}
summary(cars)
```

## Including Plots

You can also embed plots, for example:

```{r pressure, echo=FALSE}
plot(pressure)
```

Note that the `echo = FALSE` parameter was added to the code chunk to prevent printing of the R code that generated the plot.
